---
title: "Calculus in R: Derivatives and Applications"
subtitle: "Unit 3: Functions<br>Script 1: Polynomials"
author: "Dan Killian with Posit AI<br>an R translation of Mike X Cohen, Calculus in Python"
date: today
toc: true
toc-depth: 3
number-sections: false
format:
    html:
        code-fold: false
        code-tools: true
        page-layout: full
fig-height: 3
fig-width: 5
execute:
    keep-md: true
    warning: false
    message: false
editor: visual
reference-location: margin
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
library(here)
library(knitr)
source("../../Calculus with R prep.r")
```

The Python version used SymPy to represent polynomial and rational expressions symbolically before plotting. In R, polynomials are evaluated numerically using vectorised arithmetic — no symbolic engine is needed. The `polynom` package exists for formal polynomial objects, but for plotting and evaluation a loop or vectorised expression is sufficient.

## Exercise 1: Random polynomials

Generate a random degree-3 polynomial with standard-normal coefficients and plot it.

```{r}

set.seed(983)   # allow different results each run

x <- seq(-5, 5, length.out = 20)

# Random coefficients (standard normal)
coefs <- rnorm(4)

# Build polynomial: sum c_i * x^i
y <- numeric(length(x))

for (i in seq_along(coefs)) {
  y <- y + coefs[i] * x^(i - 1)
}

out <- tibble(x=x, y=y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=12))

# Build a title string showing the polynomial
terms <- mapply(function(c, i) sprintf("%+.2f x^%d", c, i), coefs, 0:3)
title_str <- paste("y =", paste(terms, collapse = " "))

p <- ggplot(out, aes(x, y)) +
  geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
  geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
  geom_line(linewidth = 1.5, color = "dodgerblue2") +
  coord_cartesian(ylim = c(-15, 5)) +
  labs(x = "x", y = "f(x)", title = title_str) +
  theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

## Exercise 2: Rational function

$$f(x) = \frac{x^2 - 2x}{x^2 - 4}$$

In Python, SymPy plotted this symbolically. In R, we evaluate numerically and set values near the singularities ($x = \pm 2$) to `NA` — this prevents `geom_line()` from drawing a spurious vertical line across the asymptotes.

```{r}

x <- seq(-3, 3, length.out = 60)

num <- x^2 - 2*x
den <- x^2 - 4

y <- num / den

# Mark values near singularities as NA to avoid vertical artifacts
y <- ifelse(abs(den) < 1e-6, NA, num / den)

out <- tibble(x=x,
              num=num,
              den=den,
              y=y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=12))

p <- ggplot(out, aes(x, y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_line(linewidth = 1, color = "dodgerblue2") +
    coord_cartesian(xlim = c(-3, 3), ylim = c(-20, 20)) +
    labs(x = "x", y = "f(x)",
       title = expression(f(x) == frac(x^2 - 2*x, x^2 - 4)),
       caption="Some sort of singularity at x = -2") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

## Exercise 3: Estimate a sine wave using polynomials

The Maclaurin series (Taylor series centered at 0) for sine:

$$\sin(x) \approx \sum_{n=1}^{N} \frac{(-1)^{n+1}\, x^{2n-1}}{(2n-1)!}$$

In Python, SymPy accumulated the series symbolically term by term. In R, we accumulate numerically — adding each term into a running total with a `for` loop. The comparison to the true `sin(x)` uses sampled points rather than a second line, making it easy to see where the approximation diverges near the edges of the domain.

Let's start with $n=1$

### n=1

```{r}

order <- 10
x <- seq(-2*pi, 2*pi, length.out = 40)

sinx <- sin(x) %>% 
    round(4)

z <- numeric(length(x))

n <- 1
z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)
y <- z

out <- tibble(x, sinx, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))


p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(min(x), max(x)),
                    ylim=c(-6.3, 6.3)) +
                    #ylim = c(floor(min(y) / 10) * 10, ceiling(max(y) / 10) * 10)) +
    scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 1)) +
    scale_y_continuous(breaks=seq(round(min(y), -1), max(y), 1)) +
    labs(x = "x", y = "f(x)",
       title = paste("Maclaurin approximation of sin(x) for n = 1"),
       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=2

```{r}
n <- 2

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))


p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +
        geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(min(x), max(x)),
                    ylim = c(floor(min(y) / 10) * 10, ceiling(max(y) / 10) * 10)) +
    scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 1)) +
    scale_y_continuous(breaks=seq(round(min(y), -1), round(max(y), -1), 10)) +
    labs(x = "x", y = "f(x)",
       title = paste("Maclaurin approximation of sin(x) for n = 2"),
       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))
```

### n=3

```{r}
n <- 3

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

out <- data.frame(n, x, y=z) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))


p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(min(x), max(x)),
                    ylim = c(max(y), min(y))) +
    scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 2)) +
    scale_y_continuous(breaks=seq(round(min(y), -1), max(y), 20)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=4

```{r}
n <- 4

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))


p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +  
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(min(x), max(x)),
                    ylim = c(floor(min(y) / 10) * 10, ceiling(max(y) / 10) * 10)) +
    scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 2)) +
    scale_y_continuous(breaks=seq(round(min(y), -1), round(max(y), -1), 20)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))
 
grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=5

```{r}
n <- 5

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))


p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +  
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(min(x), max(x)),
                    ylim = c(max(y), min(y))) +
    scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 2)) +
    scale_y_continuous(breaks=seq(round(min(y), -1), max(y), 20)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

At n = 5, the points along the x axis start to describe the sine wave. Zoom in to see.

```{r}

p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +  
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(-4,4),
                    ylim = c(-4,4)) +
    #scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 2)) +
    #scale_y_continuous(breaks=seq(round(min(y), -1), max(y), 20)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}, zoomed")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=6

```{r}

n <- 6

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))

p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) + 
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(min(x), max(x)),
                    ylim = c(-3.2, 3.2)) +
#                    min(y), max(y))) +
    scale_x_continuous(breaks=seq(round(min(x), -1), max(x), 1)) +
    scale_y_continuous(breaks=seq(round(min(y), 0), max(y), .5)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=7

```{r}

n <- 7

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))

p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(-6.3, 6.3)) +
                    #ylim = c(-3.2, 3.2)) +
#                    min(y), max(y))) +
    scale_x_continuous(breaks=seq(-6, 6, 3)) +
    scale_y_continuous(breaks=seq(round(min(y), 0), round(max(y), 0), .5)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=8

```{r}

n <- 8

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))

p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +  
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(-6.3, 6.3)) +
                    #ylim = c(-3.2, 3.2)) +
#                    min(y), max(y))) +
    scale_x_continuous(breaks=seq(-6, 6, 3)) +
    scale_y_continuous(breaks=seq(round(min(y), 0), round(max(y), 0), .5)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=9

```{r}

n <- 9

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))

p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) +  
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(-6.3, 6.3)) +
                    #ylim = c(-3.2, 3.2)) +
#                    min(y), max(y))) +
    scale_x_continuous(breaks=seq(-6, 6, 3)) +
    scale_y_continuous(breaks=seq(round(min(y), 0), round(max(y), 0), .5)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### n=10

```{r}

n <- 10

z <- z + (-1)^(n+1) * x^(2*n-1) / factorial(2*n-1)

y <- z

out <- tibble(x, y) %>%
    round(1)

tbl_grob <- tableGrob(out,
                      rows=NULL,
                      theme = ttheme_minimal(base_size=11))

p <- ggplot(out, aes(x,y)) +
    geom_hline(yintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_vline(xintercept = 0, color = "darkgoldenrod2", linewidth = 1, alpha = .5) +
    geom_point(color="dodgerblue2", size=2) +
    geom_line(color = "dodgerblue2", linewidth = 1) + 
    geom_point(aes(y=sinx),
               size=.2,
               color="grey80") +
    geom_line(aes(y=sinx),
              size=.5,
              color="grey60",
              linetype="dashed") +
    coord_cartesian(xlim = c(-6.3, 6.3)) +
                    #ylim = c(-3.2, 3.2)) +
#                    min(y), max(y))) +
    scale_x_continuous(breaks=seq(-6, 6, 3)) +
    scale_y_continuous(breaks=seq(round(min(y), 0), round(max(y), 0), .5)) +
    labs(x = "x", y = "f(x)",
       title = glue("Maclaurin approximation of sin(x) for n = {n}")) +
#       caption = "Line: Taylor series") + #     Points: sin(x)") +
    theme(axis.title.y = element_text(angle = 0, vjust = .5))

grid.arrange(p, tbl_grob, ncol = 2, widths = c(3, 1))

```

### all terms together

```{r}
x <- seq(-2*pi, 2*pi, length.out = 40)
sinx <- sin(x)
z <- numeric(length(x))

series <- matrix(NA, nrow = length(x), ncol = 9)

for (n in 1:9) {
  z <- z + (-1)^(n + 1) * x^(2*n - 1) / factorial(2*n - 1)
  series[, n] <- z
}

series <- as_tibble(series, .name_repair = ~ paste0("n=", 1:9)) |>
    mutate(x = x, sinx = sinx) |>
    relocate(x, sinx) 

seriesL <- series %>%
    pivot_longer(`n=1`:`n=9`, 
                 names_to="label",
                 values_to="y") %>%
    mutate(order=as.numeric(str_sub(label, 3,4))) %>%
    relocate(order, .before=label)

ggplot(seriesL, aes(x, y)) +
  geom_line(color = "dodgerblue", 
            size=1,
            alpha=.5) +
  geom_line(aes(y = sinx), 
            linetype = "dashed", 
            color = "grey10", 
            size=.8, 
            alpha=.4) +
  coord_cartesian(xlim=c(-6,6),
                  ylim = c(-6.2, 6.2)) +
    scale_x_continuous(breaks=seq(-6,6,2)) +
    scale_y_continuous(breaks=seq(-6,6,4)) +
  facet_wrap(~ order,
             ncol=3,
             labeller = as_labeller(function(x) paste0("n=", x))) +
  labs(x = "x", y = "f(x)") +
  faceted +
  theme(axis.title.y = element_text(angle = 0, vjust = .5),
        axis.ticks=element_blank(),
        axis.text=element_blank()) 

```

```{r}

ggplot(seriesL, aes(x, y, color = label)) +
    geom_line(linewidth = 1,
              alpha=.6,
              show.legend = F) +
    scale_color_viridis_d() +
    geom_line(aes(y=sinx),
              linetype="dashed", 
              color="grey10",
              alpha=.4,
              size=2) +
    coord_cartesian(xlim=c(-6,6),
                    ylim = c(-10,10)) +
    scale_x_continuous(breaks=seq(-6,6,2)) +
    labs(x = "x", y = "f(x)", color = NULL) +
    annotate("text", x = 6.2, y =  5.3, label = "n=1", color = virid[1]) +
    annotate("text", x = 3.9, y =  -9, label = "n=2", color = virid[2]) +
    annotate("text", x = 4.3, y = 9, label = "n=3", color = virid[3], hjust = 0) +
    annotate("text", x = 5.5, y =  -9, label = "n=4", color = virid[4], hjust = 0) +
    annotate("text", x = 5.5, y = 9, label = "n=5", color = virid[5], hjust = 0) +
    annotate("text", x = 6.1, y =  -3.5, label = "n=6", color = virid[6], hjust = 0) +
    annotate("text", x = 5.8, y = 1, label="n=7-9", color="black", hjust=0)

```

```{r}
#| fig-width: 7
#| fig-height: 4.5

sinx_df <- seriesL |> distinct(x, sinx)

anim <- ggplot(seriesL, aes(x, y, color = label, group = label)) +
  geom_line(data = sinx_df, aes(x, sinx),
            inherit.aes = FALSE,
            linetype = "dashed", color = "grey10", alpha = .6, linewidth = 1.5) +
  geom_line(linewidth = 1.2, show.legend = FALSE) +
  scale_color_viridis_d() +
  coord_cartesian(xlim = c(-6, 6), ylim = c(-10, 10)) +
  scale_x_continuous(breaks = seq(-6, 6, 2)) +
  labs(x = "x", y = "f(x)",
       title = "Maclaurin approximation of sin(x) — {closest_state} terms") +
  transition_states(order, transition_length = 1, state_length = 2) +
  shadow_mark(alpha = 0.25, linewidth = 0.6) +
  enter_fade()

animate(anim, nframes = 60, fps = 10)

```
