---
title: "Calculus in R: Derivatives and Applications"
subtitle: "Unit 3: Functions<br>Script 2: Exponential and Logarithmic Functions"
author: "Dan Killian with Posit AI<br>an R translation of Mike X Cohen, Calculus in Python"
date: today
toc: true
toc-depth: 3
number-sections: false
format:
    html:
        code-fold: false
        code-tools: true
        page-layout: full
fig-height: 3
fig-width: 5
execute:
    keep-md: true
    warning: false
    message: false
editor: visual
reference-location: margin
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
library(here)
library(knitr)
source("../../Calculus with R prep.r")
```

# Exercise 1: Estimate *e*

Where does *e* come from?

There are several ways to express / define *e*. Here's the way to express it in terms of limits. 

$$e=\lim_{n\to\infty}\left(1+\frac{1}{n}\right)^n$$


```{r}
n <- 1:90

exp_est <- tibble(n,
                  e_est=NA, 
                  e_diff=NA)

for (i in n) {
  exp_est$e_est[i] <- (1 + 1/n[i])^n[i]
  exp_est$e_diff[i] = exp(1) - exp_est$e_est[i]
}
```

:::{.columns}

:::{.column width="33%"}
```{r}
exp_est %>%
    head(30) %>%
    flextable()
```
:::

::: {.column width="33%"}
```{r}
exp_est %>%
    .[31:60,] %>%
    flextable()
```
:::

::: {.column width="33%"}
```{r}
exp_est %>%
    tail(30) %>%
    flextable()
```
:::

:::

The value of *n* must get into the hundreds before the estimate will converge to 2.72


# Exercise 2: Visualize *e*'s convergence

Plot the convergence of the estimate to *e*

```{r}
ggplot(exp_est, aes(n, e_diff)) +
    geom_hline(yintercept=.0183,
               color="grey60",
               alpha=.4,
               size=1) +
    geom_line(color="indianred",
              size=1, 
              alpha=.5) +
    scale_x_continuous(breaks=seq(0,90, 10)) +
    scale_y_continuous(breaks=seq(0,.8,.1)) +
    labs(x = "n", 
         y = "Error",
         title = "Convergence of (1 + 1/n)^n to e") +
    theme(axis.title.y=element_text(angle=0, 
                                    vjust=.5))
```
At what point does the sequence converge? Let's say reaching 2.7 is close enough to be considered as reaching 2.718

```{r}
ggplot(filter(exp_est, n>39), aes(n, e_diff)) +
    geom_hline(yintercept=.0183,
               color="grey60",
               alpha=.4,
               size=1) +
    geom_line(color="indianred",
              size=1, 
              alpha=.5) +
    coord_cartesian(ylim=c(0,.035), xlim=c(40,90)) +
    scale_x_continuous(breaks=seq(40,90, 5)) +
    scale_y_continuous(breaks=seq(0,.05,.005)) +
    labs(x = "n", 
         y = "Error",
         title = "Convergence of (1 + 1/n)^n to e") +
    theme(axis.title.y=element_text(angle=0, 
                                    vjust=.5))
```
The estimate reaches 2.7 at about $n=73$. The value of $n$ needs to be 164 to reach 2.71, and 4,822 to reach 2.718

# Exercise 3: Exploring *e* in R

Plot a family of exponential functions

```{r}
x <- seq(-2,2, length.out = 20)
e_x <- exp(x)
e_x2 <- exp(x^2)
e_x22 <- exp((-x)^2)
e_negx2 <- exp(-(x^2))
ex2 <- exp(x)^2

func_key <- tibble(func_code = 1:5,
                   func=c("e_x","e_x2","e_x22","e_negx2","ex2"),
                   `function` = c("$e^x$",
                                  "$e^{x^2}$",
                                  "$e(-x)^2$",
                                  "$e^{-(x^2)}$",
                                  "$(e^x)^2$"))


#func_key

d <- tibble(x, e_x, e_x2, e_x22, e_negx2, ex2)

dL <- d %>%
    pivot_longer(-x,
                 names_to="func",
                 values_to="y") %>%
    left_join(func_key, by = "func") 

dL %>%
    head() %>%
    kable(escape=T)
```

```{r}
ggplot(dL, aes(x, y, color = func)) +
    geom_line(size=1,
              alpha=.6) +
    coord_cartesian(xlim = c(-2,2), ylim = c(0,10)) +
    scale_y_continuous(breaks=seq(0,10,2))

```

# Exercise 4: Exploring *e* in R (symbolic-style expression)

In Python, SymPy plotted `exp(beta) - log(beta) - e` symbolically.
In R we evaluate and plot the same function directly over a numeric grid.

```{r}
beta <- seq(0.01, 2, length.out = 200)   # avoid log(0)
y    <- exp(beta) - log(beta) - exp(1)

ggplot(data.frame(beta = beta, y = y), aes(beta, y)) +
    geom_hline(yintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
    geom_vline(xintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
  geom_line(linewidth = 1, 
            color="darkgoldenrod2") +
  labs(x = expression(beta),
       y = expression(f(beta)),
       title = expression(f(beta) == e^beta - log(beta) - e)) +
    theme(axis.title.y=element_text(angle=0,
                                    vjust=.6))
```

# Exercise 5: Exp and log as mutual inverses

```{r}
x_log <- seq(0.001, 4, length.out = 30)
x_exp <- seq(-4, 4, length.out = 30)

df <- rbind(
  data.frame(x = x_log, y = log(x_log),              fun = "log(x)"),
  data.frame(x = x_exp, y = exp(x_exp),              fun = "exp(x)"),
  data.frame(x = x_exp, y = log(exp(x_exp)),         fun = "log(exp(x))"),
  data.frame(x = x_exp, y = exp(log(x_exp)),         fun = "exp(log(x))")
)

ggplot(df, aes(x = x, y = y, color = fun, shape = fun)) +
    geom_hline(yintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
    geom_vline(xintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
    geom_line(size=.8) +
    geom_point(size = 1.5) +
    coord_fixed(xlim = c(-4, 4), ylim = c(-4, 4)) +
    labs(x = "x", y = "y", color = NULL, shape = NULL) +
    theme(axis.title.y=element_text(angle=0,
                                    vjust=.5))
```
