---
title: "Calculus in R: Derivatives and Applications"
subtitle: "Unit 3: Functions<br>Script 2: Exponential and Logarithmic Functions"
author: "Dan Killian with Posit AI<br>an R translation of Mike X Cohen, Calculus in Python"
date: today
toc: true
toc-depth: 3
number-sections: false
format:
    html:
        code-fold: false
        code-tools: true
        page-layout: full
fig-width: 3
fig-height: 5
execute:
    keep-md: true
    warning: false
    message: false
editor: visual
reference-location: margin
---

```{r global_options, include=F, warning=F, message=F, echo=F, error=F}
library(here)
library(knitr)
source("../../Calculus with R prep.r")
```

# Exercise 1: Estimate *e*

Where does *e* come from?

There are several ways to express / define *e*. Here's the way to express it in terms of limits. 

$$e=\lim_{n\to\infty}\left(1+\frac{1}{n}\right)^n$$


```{r}
n_vals <- c(1, 2, 5, 10)
n <- 1:90

exp_est <- tibble(n,
                  e_est=NA, 
                  e_diff=NA)

for (i in n) {
  exp_est$e_est[i] <- (1 + 1/n[i])^n[i]
  exp_est$e_diff[i] = exp(1) - e_est[i]
}
```

:::{.columns}

:::{.column width="33%"}
```{r}
exp_est %>%
    head(30) %>%
    flextable()
```
:::

::: {.column width="33%"}
```{r}
exp_est %>%
    .[31:60,] %>%
    flextable()
```
:::

::: {.column width="33%"}
```{r}
exp_est %>%
    tail(30) %>%
    flextable()
```
:::

:::

# Exercise 2: Visualize *e*'s convergence

```{r}
n <- 1:1000
e_diffs <- exp(1) - (1 + 1/n)^n

ggplot(data.frame(n = n, diff = e_diffs), aes(n, diff)) +
  geom_line(linewidth = 1) +
  labs(x = "n", y = "Difference to exp(1)",
       title = "Convergence of (1 + 1/n)^n to e")
```

# Exercise 3: Exploring *e* in R

```{r}
x_domain <- c(-2, 2)
x <- seq(x_domain[1], x_domain[2], length.out = 41)

data.frame(
  x   = x,
  `e^x`          = exp(x),
  `e^(x^2)`      = exp(x^2),
  `e^((-x)^2)`   = exp((-x)^2),
  `exp(-(x^2))`  = exp(-(x^2)),
  `exp(x)^2`     = exp(x)^2,
  check.names = FALSE
) |>
  pivot_longer(-x, names_to = "fun", values_to = "y") |>
  ggplot(aes(x = x, y = y, color = fun)) +
  geom_line(linewidth = 1) +
  coord_cartesian(xlim = x_domain, ylim = c(-1, 10)) +
  labs(x = "x", y = "y = f(x)", color = NULL) +
  theme(legend.position = "right")
```

# Exercise 4: Exploring *e* in R (symbolic-style expression)

In Python, SymPy plotted `exp(beta) - log(beta) - e` symbolically.
In R we evaluate and plot the same function directly over a numeric grid.

```{r}
beta <- seq(0.01, 2, length.out = 200)   # avoid log(0)
y    <- exp(beta) - log(beta) - exp(1)

ggplot(data.frame(beta = beta, y = y), aes(beta, y)) +
    geom_hline(yintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
    geom_vline(xintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
  geom_line(linewidth = 1, 
            color="darkgoldenrod2") +
  labs(x = expression(beta),
       y = expression(f(beta)),
       title = expression(f(beta) == e^beta - log(beta) - e)) +
    theme(axis.title.y=element_text(angle=0,
                                    vjust=.6))
```

# Exercise 5: Exp and log as mutual inverses

```{r}
x_log <- seq(0.001, 4, length.out = 30)
x_exp <- seq(-4, 4, length.out = 30)

df <- rbind(
  data.frame(x = x_log, y = log(x_log),              fun = "log(x)"),
  data.frame(x = x_exp, y = exp(x_exp),              fun = "exp(x)"),
  data.frame(x = x_exp, y = log(exp(x_exp)),         fun = "log(exp(x))"),
  data.frame(x = x_exp, y = exp(log(x_exp)),         fun = "exp(log(x))")
)

ggplot(df, aes(x = x, y = y, color = fun, shape = fun)) +
    geom_hline(yintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
    geom_vline(xintercept = 0,
               size=1,
               color="grey60",
               alpha=.6) +
    geom_line(size=.8) +
    geom_point(size = 1.5) +
    coord_fixed(xlim = c(-4, 4), ylim = c(-4, 4)) +
    labs(x = "x", y = "y", color = NULL, shape = NULL) +
    theme(axis.title.y=element_text(angle=0,
                                    vjust=.5))
```
